### 2020-02-07 README.rmd
Fixes README figure resolution
Adds ROS logo to README

You can install
[Rclean](https://cran.r-project.org/web/packages/Rclean/) from *CRAN*:

```{r eval = FALSE}
install.packages("Rclean")
```

@@

```{r eval = FALSE} 
script <- "example/simple_script.R"

@@

@@

>>>>

@@

```{r eval = FALSE} 
script <- system.file("example", "simple_script.R", package = "Rclean")

@@

```{r eval = TRUE, out.width = "75%", dpi = 300}

@@

![ropensci_footer](https://ropensci.org/public_images/ropensci_footer.png)
